Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Unanon.

\title{Optimizing Abstract Abstract Machines
\vskip -1.5cm}

%% \authorinfo{J. Ian Johnson}
%%            {Northeastern University}
%%            {ianj@ccs.neu.edu}
%% \authorinfo{Matthew Might}
%%            {University of Utah}
%%            {might@cs.utah.edu}
%% \authorinfo{David Van Horn}
%%            {Northeastern University}
%%            {dvanhorn@ccs.neu.edu}
\authorinfo{}{}{}

@@

The analysis considered here computes results similar Earl, et al.'s
0-CFA implementation, which times out on the \Church{} benchmark
because it does not widen the store as described for our baseline
evaluator.  So even though it offers a fair point of comparison, a
more thorough evaluation is probably uninformative as the other
benchmarks are likely to timeout as well (and it would require
significant effort to extend their implementation with the features
needed to analyze our benchmark suite).  That implementation is
evaluated against much smaller benchmarks: the largest program is 30
lines.

>>>>

\title{Optimizing Abstract Abstract Machines}

\authorinfo{J. Ian Johnson}
           {Northeastern University}
           {ianj@ccs.neu.edu}
\authorinfo{Matthew Might}
           {University of Utah}
           {might@cs.utah.edu}
\authorinfo{David Van Horn}
           {Northeastern University}
           {dvanhorn@ccs.neu.edu}

@@

The analysis considered here computes results similar Earl, et al.'s
0-CFA implementation~\cite{dvanhorn:Earl2012Introspective}, which
times out on the \Church{} benchmark because it does not widen the
store as described for our baseline evaluator.  So even though it
offers a fair point of comparison, a more thorough evaluation is
probably uninformative as the other benchmarks are likely to timeout
as well (and it would require significant effort to extend their
implementation with the features needed to analyze our benchmark
suite).  That implementation is evaluated against much smaller
benchmarks: the largest program is 30 lines.
